---
title: 'Bringing Python and R Together'
subtitle: 
summary:
authors:
- admin
tags:
- 
categories: []
date: "2020-03-07T00:00:00Z"
featured:
draft: true

# Featured image
# To use, add an image named `featured.jpg/png` to your page's folder.
# Placement options: 1 = Full column width, 2 = Out-set, 3 = Screen-width
# Focal point options: Smart, Center, TopLeft, Top, TopRight, Left, Right, BottomLeft, Bottom, BottomRight
header:
  caption: ''
  image: ''
  
image:
  placement: 2
  caption:
  focal_point: Top
  preview_only: false
---

Two most influential programming languages for machine learning, data science and visualization are Python and R. And there has been a tough competition between the two. Both are great and has their own superiority over each other. However, thanks to the R `reticulate` package it is now possible to work on both languages at the same time. As a text editor, RStudio is a well-suited environment to work on both. In this post I want to share shortly how to do so.  

# R Environment
Lets load the regular libraries in R

```{r}
knitr::opts_chunk$set(message = FALSE, warning=FALSE, echo = TRUE, cache = FALSE)
```


```{r setup, include=FALSE}
library(wooldridge)
library(tidyverse)
library(patchwork)
theme_set(theme_light())
```

After that we use the library `reticulate` and `use_condaenv("r-reticulate")`. These two functions let us use R and python together and work on the same data set. 

```{r}
library(reticulate)
use_condaenv("r-reticulate")
```

For the first round, we load the `woolridge` data set. This data set are mostly used for labor economics. Here we look at the relationship between education, wages and experience. 

```{r}
we <- wooldridge::wage1

p1 <- we%>%
  ggplot()+
  geom_point(aes(educ, lwage))+
  geom_smooth(aes(educ, lwage))+
  labs(caption = "Source: Woolridge Data Set")

p2 <- we%>%
  ggplot()+
  geom_point(aes(exper, lwage))+
  geom_smooth(aes(exper, lwage))+
  labs(caption = "Source: Woolridge Data Set")

p1 + p2
```

# Python Environment
First we load python libraries, and their styles.
```{python}
import numpy as np
import matplotlib.pyplot as plt
plt.style.use('seaborn')
```


> An important point to mention is that when we use the data in python that we already used in R we simply call it by `r.dataset` . In the opposite case (when we use data in R that we already prepared in python), we use the option `py$dataset` . This two functions make the life much easier than we think. 


```{python}
we_py = r.we

plt.subplot(2,1,1)
plt.scatter(we_py['educ'], we_py['lwage'])
plt.xlabel('Education')
plt.ylabel('Log Wage')

plt.subplot(2,1,2)
plt.scatter(we_py['exper'], we_py['lwage'])
plt.xlabel('Experience')
plt.ylabel('Log Wage')
plt.show()
```

## Result
We do not necessarily have to work on different languages and miss on the great functionality provided by both languages. Fortunately, `reticulate` package in R solves the problem. Now we are able to benefit from both python and R for our research. 







